---
title: "Time series analysis"
author: "Oliver Ørskov"
date: "28/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
library(xts)
library(RColorBrewer)
library(plotly)
library(lme4)
library(forecast)

setwd("~/Documents/Skole/CogSci kandidat/2. Semester/Data Science/Exam")


```



```{r}
# load data

data_long <- read.csv("~/Documents/Skole/CogSci kandidat/2. Semester/Data Science/Exam/sales_2016-01-01_2020-04-27.csv")

# convert to wide format
# start by dropping total_sales
data_long <- within(data_long, rm(total_sales, variant_title))

# aggregate where there are multiple of the same sales on the same dates
data_long <- aggregate(net_quantity ~ day + product_title, data = data_long, FUN = 'sum')
data_long$weekday <- as.factor(as.POSIXlt(data_long$day)$wday)
data_long$day <- as.Date(data_long$day)

#convert
data <- spread(data_long, product_title, net_quantity)

# remove V1
data <- within(data, rm(V1))

# convert date to actual datetime format
data$day <- as.Date(data$day)

# save dataset
write.csv(data,"bakesales.csv", row.names = FALSE)

# What are the top selling baked goods?
data_sum <- data
data_sum <- within(data_sum, rm(day, weekday))
data_sum <- colSums(data_sum, na.rm = TRUE)
data_sum <- as.data.frame(data_sum)
library(data.table)
data_sum <- setDT(data_sum, keep.rownames = TRUE)[]

# ORDER
colnames(data_sum) <- c("item_name","total_sales")
data_sum <- data_sum[order(-data_sum$total_sales),]
data_sum$item_name <- factor(data_sum$item_name)
data_sum$item_name <- data_sum$item_name[order(-data_sum$total_sales)]

# PLOT TOP SELLERS
ggplot(data = data_sum[1:20,], aes(x=item_name, y=total_sales)) + 
  geom_col(width=.5, fill="tomato3", aes(reorder(item_name,-total_sales),total_sales), stat = 'identity') +
  labs(title="Top 20 best selling items") +
  theme(axis.text.x = element_text(angle=60, vjust=0.6)) +
  xlab("Item") +
  ylab("Nuber of total sales")


# Remove spaces from column names
library(stringr)
names(data)<-str_replace_all(names(data), c(" " = "_"))

# plotting time series
par(mfrow=c(1,1))
plot(data$day,data$Landbrød, type = "b")

# nicer plot
  plot <- ggplot(data,aes(day,Landbrød)) +
          geom_line(data = data,aes(day,Landbrød, color= "Landbrød")) +
          geom_line(data = data,aes(day,Croissant, color = "Croissant")) +
          geom_line(data = data,aes(day,Almond_Croissant, color = "Almond Croissant")) +
          geom_line(data = data,aes(day,Kardemommesnurre, color = "Kardemommesnurre")) +
          geom_line(data = data,aes(day,Banana_Bread, color = "Banana Bread")) +
          geom_line(data = data,aes(day,Kanelsnegl, color = "Kanelsnegl")) +
          geom_line(data = data,aes(day,Cookie, color = "Cookie")) +
          geom_line(data = data,aes(day,Hindbærsnitte, color = "Hindbærsnitte")) +
          geom_line(data = data,aes(day,Surdejsstykke, color = "Surdejsstykke")) +
          geom_line(data = data,aes(day,Pain_au_chocolat, color = "Pain au chocolat")) +
          theme_minimal() + 
          labs(color="Legend text") +
          ggtitle("Sales per day") +
          xlab("Date range") + 
          ylab("Number of items sold") #+
         # scale_color_brewer(palette="RdYlBu")
  plot

# Turn it interactive with ggplotly
plot <- ggplotly(plot)
plot

# PLOTTING ONLY LANDBRØD AND CROISSANTS
plot <- ggplot(data,aes(day,Landbrød)) +
        geom_line(aes(color="Landbrød")) +
        geom_line(data = data,aes(day,Croissant, color = "Croissant")) +
        geom_line(data = data,aes(day,Almond_Croissant, color = "Almond Croissant")) +
        theme_minimal() + 
        labs(color="Legend text") +
        ggtitle("Sales per day") +
        xlab("Date range") + 
        ylab("Number of items sold")# +
        #scale_color_brewer(palette="Set2")
plot

# Turn it interactive with ggplotly
plot <- ggplotly(plot)
plot

```

# PLOT BY WEEKDAY
```{r}
data$weekday <- as.factor(as.POSIXlt(data$day)$wday)

p <- ggplot(data, aes(x=weekday, y=Landbrød)) + 
  geom_boxplot()
p

# plotting by the long data format

sub <- data_long[data_long$product_title == "Landbrød"|
                 data_long$product_title == "Croissant"|
                data_long$product_title == "Almond Croissant"
                   ,]

p <- ggplot(sub, aes(x=weekday, y=net_quantity, fill = product_title)) + 
  geom_boxplot() +
  ggtitle("Sales per weekday") +
  xlab("Day of week") + 
  ylab("Average number of items sold")
p



```

# ADD WEATHERDATA TO THE DATASET

```{r}
# Trying to load this datafile from https://rp5.ru/Weather_archive_in_Tirstrup_(airport),_METAR
weather_data <- read.csv("~/Documents/Skole/CogSci kandidat/2. Semester/Data Science/Exam/EKAH.01.01.2016.27.04.2020.1.0.0.en.utf8.00000000.csv", sep=";", comment.char="#")

# rename columns
weather_data <- weather_data %>% 
  rename(
    time = "Local.time.in.Tirstrup..airport.",
    temp = "T",
    pressure = "P0"
    )
weather_data

keep <- as.vector(c("time",
                    "temp",
                    "pressure"
                    ))
keep                                 

weather_data <- weather_data[,keep]       # Extracting only three
weather_data

# as dattime format
weather_data$day <- as.POSIXct(weather_data$time,format="%d.%m.%Y")    # %H:%M

# get average temperature per day
library(dplyr)
library(lubridate)

# add mean temp
mean_temp <- weather_data %>%
  mutate(date = floor_date(day)) %>%
  group_by(day) %>%
  summarize(mean_temp = mean(temp))

# add mean pressure
mean_pressure <- weather_data %>%
  mutate(date = floor_date(day)) %>%
  group_by(day) %>%
  summarize(mean_pressure = mean(pressure))



## ADD THIS TO THE DATASET

data$mean_temp <- mean_temp$mean_temp[1:1579]
data$mean_pressure <- mean_pressure$mean_pressure[1:1579]

# plot the temperature

# Area chart with temperature and pressure
p <- plot_ly(x = data$day, y = data$mean_temp, type="scatter", mode="lines", name = "Daily mean temp")
p <- add_trace(p, x = data$day, y = data$mean_pressure, type="scatter", mode="lines", name = "Daily mean pressure", yaxis = "y2")

# second y-axis
ay <- list(
  tickfont = list(color = "orange"),
  overlaying = "y",
  side = "right",
  title = "Pressure (mmHg)"
)

p <- p %>% layout(
    title = "Aarhus Weather", yaxis2 = ay,
    xaxis = list(title="date")
  )

p

# indication that pressure and precipitation is negatively correlated:
# https://ui.adsabs.harvard.edu/abs/2018AGUFM.H43H2543Y/abstract


```


# just checking if pressure and landbrød sales is correlated
```{r}
cor(data$mean_pressure, data$Landbrød, use = "complete.obs")

# landbrød
linearModel <- lm(Landbrød ~ mean_pressure + mean_temp, data=data)
summary(linearModel)

#what about for croissants?
linearModel <- lm(Croissant ~ mean_pressure + mean_temp, data=data)
summary(linearModel)

#what about for almond croissants?
linearModel <- lm(Almond_Croissant ~ mean_pressure + mean_temp, data=data)
summary(linearModel)

# this is predicted line comparing only chosen variables
ggplot(data = data, aes(x = mean_temp, y = Landbrød)) + 
  geom_point(color='blue') +
  geom_smooth(method = "lm", se = FALSE, color="red")

# this is predicted line comparing only chosen variables
ggplot(data = data, aes(x = mean_pressure, y = Landbrød)) + 
  geom_point(color='blue') +
  geom_smooth(method = "lm", se = FALSE, color="red")


# SO WHAT THIS MEANS:
# THE HIGHER THE TEMPERATURE, THE MORE LANDBRØD-SALES
# THE HIGHER THE PRESSURE, THE FEWER LANDBRØD-SALES

```


# SO FAR SO GOOD!


# forecasting using the online book: https://otexts.com/fpp3/
```{r}

library(fpp3)

tsibble <- as_tsibble(data)
tsibble$day <- as_date(tsibble$day)

# a tsibble allows for multiple time series in a single object

# plot landbrød
tsibble %>%
  autoplot(Landbrød) +
    labs(title = "Sales of landbrød", subtitle = "subtitle") +
    xlab("Year") +
    ylab("Daily number of sales")

# plot temperature
tsibble %>% autoplot(mean_temp) +
  ggtitle("Daily mean temperature") +
  ylab("Temperature (c)") + xlab("Year")


# Seasonal plots
tsibble %>% gg_season(Landbrød) +
  ylab("Daily number of sales") +
  ggtitle("Seasonal plot: Sales of landbrød")

# multiple seasonal periods
tsibble %>% gg_season(Landbrød, period="week")
tsibble %>% gg_season(Landbrød, period="month")
tsibble %>% gg_season(Landbrød, period="year")

tsibble %>% gg_season(mean_temp, period="week")
tsibble %>% gg_season(mean_temp, period="month")
tsibble %>% gg_season(mean_temp, period="year")

tsibble %>% gg_season(Croissant, period="week")
tsibble %>% gg_season(Croissant, period="month")
tsibble %>% gg_season(Croissant, period="year")

# fastelavnsbolle only in feb/march
tsibble %>% gg_season(Fastelavnsbolle, period="week")
tsibble %>% gg_season(Fastelavnsbolle, period="month")
tsibble %>% gg_season(Fastelavnsbolle, period="year")

# honningkage only in december
tsibble %>% gg_season(Honningkage, period="week")
tsibble %>% gg_season(Honningkage, period="month")
tsibble %>% gg_season(Honningkage, period="year")

#æblekage only fall 2017
tsibble %>% gg_season(Æblekage, period="week")
tsibble %>% gg_season(Æblekage, period="month")
tsibble %>% gg_season(Æblekage, period="year")

# Seasonal subseries plots
tsibble %>%
  gg_subseries(Landbrød) +
    ylab("Number of sales") +
    xlab("Year") +
    ggtitle("Seasonal subseries plot: Landbrød sales")


# plot scatter plots with temperature and sales against oneanother

tsibble %>%
  ggplot(aes(x = mean_temp, y = Landbrød)) +
    geom_point() +
    ylab("Sales") + xlab("Temperature (Celsius)")

library(GGally)

data_long %>%
  spread(product_title, net_quantity) %>%
  GGally::ggpairs(columns = 2:9)

tsibble %>% ACF(Landbrød, lag_max = 365) %>% autoplot()

```

# Chapter 3 Time series decomposition

```{r}
# replace NA's with 0 and select landbrød
landbrød_only <- tsibble %>%
  select(Landbrød)

landbrød_only[is.na(landbrød_only)] <- 0

landbrød_only %>%
  autoplot(Landbrød) +
  xlab("Year") + ylab("Persons (thousands)") +
  ggtitle("Total employment in US retail")


# STL decomposition - “Seasonal and Trend decomposition using Loess” - Landbrød
dcmp <- landbrød_only %>%
  model(STL(Landbrød))
components(dcmp)

# plot the decomposition
# The trend column (containing the trend-cycle  Tt) follows the overall movement of the series, ignoring any seasonality and random fluctuations, as shown in this next figure.

landbrød_only %>%
  autoplot(Landbrød, color='gray') +
  autolayer(components(dcmp), trend, color='red') +
  xlab("Year") + ylab("Number of daily sold items") +
  ggtitle("Bread sales....")

# plotting all the components of the decomposition
components(dcmp) %>% autoplot() + xlab("Year")

## ------------------

# replace NA's with 0 and select croissant
croissant_only <- tsibble %>%
  select(Croissant)

croissant_only[is.na(croissant_only)] <- 0

# STL decomposition - “Seasonal and Trend decomposition using Loess” - Croissant!
dcmp <- croissant_only %>%
  model(STL(Croissant))
components(dcmp)

# plotting all the components of the decomposition
components(dcmp) %>% autoplot() + xlab("Year")

## ------------------

# replace NA's with 0 and select almond croissant
almond_croissant_only <- tsibble %>%
  select(Almond_Croissant)

almond_croissant_only[is.na(almond_croissant_only)] <- 0

# STL decomposition - “Seasonal and Trend decomposition using Loess” - Almond Croissant!
dcmp <- almond_croissant_only %>%
  model(STL(Almond_Croissant))
components(dcmp)

# plotting all the components of the decomposition
components(dcmp) %>% autoplot() + xlab("Year")



# Seasonally adjusted data
landbrød_only %>%
  autoplot(Landbrød, color='gray') +
  autolayer(components(dcmp), season_adjust, color='blue') +
  xlab("Year") + ylab("Number of daily items sold") +
  ggtitle("Daily landbrød sales")


# this one for specifying parameters manually
landbrød_only %>%
  model(STL(Landbrød ~ trend(window=31) + season(window='periodic'),
    robust = TRUE)) %>%
  components() %>%
  autoplot()


```


# Forecasting with decomposition

```{r}

# replace NA's with 0 and select landbrød

whatever_data <- tsibble %>%
  select(Landbrød) 

whatever_data[is.na(whatever_data)] <- 0

dcmp <- whatever_data %>%
  model(STL(Landbrød ~ trend(window = 7), robust=TRUE)) %>%
  components() %>%
  select(-.model)
dcmp %>%
  model(NAIVE(season_adjust)) %>%
  forecast() %>%
  autoplot(dcmp) + ylab("New orders index") +
  ggtitle("Naive forecasts of seasonally adjusted data")

## Forecasts based on a naïve forecast of the seasonally adjusted data and a seasonal naïve forecast of the seasonal component, after an STL decomposition of the data.

fit_dcmp <- whatever_data %>%
  model(stlf = decomposition_model(
             STL(Landbrød ~ trend(window = 7), robust = TRUE),
             NAIVE(season_adjust)))
fit_dcmp %>%
  forecast() %>%
  autoplot(whatever_data)

# just trying to see if we can turn this into weekly data

weekly_sales <- data_long_tsibble %>%
  group_by_key() %>%
  index_by(Year_Week = ~ yearweek(.)) %>%
  summarise(
    sales = max(net_quantity)
  )

# doing the same forecast with weekly data

landbrød_weekly <- tsibble %>%
  select(day, Landbrød) %>%
  group_by_key() %>%
  index_by(Year_Week = ~ yearweek(.)) %>%
  summarise(
    sales = mean(Landbrød)
  )

landbrød_weekly[is.na(landbrød_weekly)] <- 0

fit_dcmp <- landbrød_weekly %>%
  model(stlf = decomposition_model(
             STL(sales ~ trend(window = 7), robust = TRUE),
             NAIVE(season_adjust)))
fit_dcmp %>%
  forecast() %>%
  autoplot(landbrød_weekly)

```

# exponential smoothing with trend
```{r}

fit <- landbrød_data %>%
  model(AAN = ETS(Landbrød ~ error("A") + trend("A") + season("N")))
fc <- fit %>% forecast(h = 10)
fc

# the forecasts for 2 months generated from Holt’s linear trend method and the damped trend method.

landbrød_data %>%
  model(
    `Holt's method` = ETS(Landbrød ~ error("A") + trend("A") + season("N")),
    `Damped Holt's method` = ETS(Landbrød ~ error("A") + trend("Ad", phi = 0.9) + season("N"))
  ) %>%
  forecast(h = 60) %>%
  autoplot(landbrød_data, level = NULL) +
  ggtitle("Forecasts from Holt's method") + xlab("Year") +
  ylab("Daily number of sold items") +
  guides(colour = guide_legend(title = "Forecast"))


# Forecasting landbrød sales using the Holt-Winters method with both additive and multiplicative seasonality.

fit <- landbrød_data %>%
  model(
    additive = ETS(Landbrød ~ error("A") + trend("A") + season("A")),
    multiplicative = ETS(Landbrød ~ error("M") + trend("A") + season("M"))
  )
fc <- fit %>% forecast(h = "1 year")

fc %>%
  autoplot(landbrød_data, level = NULL) + xlab("Year") +
  ylab("Overnight trips (millions)") +
  scale_color_brewer(type = "qual", palette = "Dark2")

# I don't know why the multiplicative is not working, but the additive seems to be a valid model..

# Example: Holt-Winters method with daily data

landbrød_data %>%
  model(hw = ETS(Landbrød ~ error("M") + trend("Ad") + season("M"))) %>%
  forecast(h = "2 weeks") %>%
  autoplot(landbrød_data) #... not working???

# 8.4 A taxonomy of exponential smoothing methods
# apparently there are 9 different kinds of exponential smoothing methods.. figure out which one is the best for this


```


# ARIMA models

```{r}

library(urca)

fit <- landbrød_data %>%
  model(ARIMA(Landbrød ~ PDQ(0,0,0)))
report(fit)

fit %>% forecast(h=10) %>% autoplot(slice(landbrød_data, (n()-30):n()))
# looks pretty good I guess...

# An ARIMA(2,1,3) model was automatically selected.. what does this mean?
# p = order of the autoregressive part;
# d = degree of first differencing involved;
# q = order of the moving average part.

# so a model with 2nd order autoregressive part,
# 1st degree of first differencing involved
# 3rd order of the moving average part..

# looking at difference, acf and pacf

landbrød_data %>%
  gg_tsdisplay(difference(Landbrød), plot_type='partial')

# there is definitely a 7 day lag thing...


# AUTO ARIMA
fit.arima <- auto.arima(landbrød_data_train$Landbrød, seasonal = TRUE, ic = "aicc")    # auto arima with forced seasonality
fit.arima


############## --------------- ######################

# SEASONAL ARIMA

# Fitting models, selecting models, evaluating models ##

############# ----------------#######################

# Set training data from 2016 to 2019
landbrød_data_train <- landbrød_data %>%
  filter_index("2016" ~ "2019")

# Set test set data from 2016 to 2019
landbrød_data_test <- landbrød_data %>%
  filter_index("2020" ~ "2021")



#### (1,1,1)(0,0,2)[7]  SUGGESTED MODEL #####

fit <- landbrød_data_train %>%
  model(arima = ARIMA(Landbrød ~ 0 + pdq(1,1,1) + PDQ(0,0,2)))

report(fit)
fit %>% forecast(h=118) %>% autoplot(slice(landbrød_data, (n()-118):n()))
fc <- fit %>% forecast(h=118)
# Generate forecasts and compare accuracy over the test set
fc <- fit %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc[,c("RMSE","MAE","MAPE","MASE")]

#### (1,1,1)(0,1,1)[7]

fit5 <- landbrød_data_train %>%
  model(arima = ARIMA(Landbrød ~ 0 + pdq(1,1,1) + PDQ(0,1,1)))
#fit5 %>% gg_tsresiduals()
report(fit5)
fit5 %>% forecast(h=118) %>% autoplot(slice(landbrød_data, (n()-118):n()))
fc5 <- fit5 %>% forecast(h=118)
# Generate forecasts and compare accuracy over the test set
fc5 <- fit5 %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc5[,c("RMSE","MAE","MAPE","MASE")]


#### (1,1,1)(1,1,1)[7] ----------- best model!!

fit6 <- landbrød_data_train %>%
  model(arima = ARIMA(Landbrød ~ 0 + pdq(1,1,1) + PDQ(1,1,1)))

report(fit6)
fit6 %>% forecast(h=118) %>% autoplot(slice(landbrød_data, (n()-180):n()))
fc6 <- fit6 %>% forecast(h=118)
# Generate forecasts and compare accuracy over the test set
fc6 <- fit6 %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc6[,c("RMSE","MAE","MAPE","MASE")]
fit6 %>% gg_tsresiduals()


#### (1,1,2)(0,1,1)[7]

fit7 <- landbrød_data_train %>%
  model(arima = ARIMA(Landbrød ~ 0 + pdq(1,1,2) + PDQ(0,1,1)))

report(fit7) 
fit7 %>% forecast(h=118) %>% autoplot(slice(landbrød_data, (n()-118):n()))
fc7 <- fit7 %>% forecast(h=118)
# Generate forecasts and compare accuracy over the test set
fc7 <- fit7 %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc7[,c("RMSE","MAE","MAPE","MASE")]


#### (0,1,7)(0,1,0)[7] 

fit9 <- landbrød_data_train %>%
  model(arima = ARIMA(Landbrød ~ 0 + pdq(0,1,7) + PDQ(0,1,0)))

report(fit9)
fit9 %>% forecast(h=118) %>% autoplot(slice(landbrød_data, (n()-118):n()))
fc9 <- fit9 %>% forecast(h=118)
# Generate forecasts and compare accuracy over the test set
fc9 <- fit9 %>% forecast(h=118) %>%
  accuracy(landbrød_data) 
fc9[,c("RMSE","MAE","MAPE","MASE")]

#### (0,1,8)(0,1,0)[7] 

fit10 <- landbrød_data_train %>%
  model(arima = ARIMA(Landbrød ~ 0 + pdq(0,1,8) + PDQ(0,1,0)))

report(fit10)
fit10 %>% forecast(h=118) %>% autoplot(slice(landbrød_data, (n()-118):n()))
fc10 <- fit10 %>% forecast(h=118)
# Generate forecasts and compare accuracy over the test set
fc10 <- fit10 %>% forecast(h=118) %>%
  accuracy(landbrød_data) 
fc10[,c("RMSE","MAE","MAPE","MASE")]


# LET'S USE THIS ONE FOR FORECASTING

landbrød_fc <- fit %>% forecast(h=100) %>% autoplot(slice(landbrød_data, (n()-30):n()))
landbrød_fc

# Plot forecasts against actual values

# Set training data from 2016 to 2019
train <- landbrød_data %>%
  filter_index("2016" ~ "2019")


######### ----------- ETS ----------- #############


# Automatically find the best ETS model in the data

fit <- landbrød_data %>%
  model(ETS(Landbrød))
fc <- fit %>% forecast(h = "1 year")
report(fit)

# Model: ETS(A,N,A) 
#  Smoothing parameters:
#    alpha = 0.1207525 
#    gamma = 0.1148749 

## MAIN MODEL ^^^^


# ANA

fit1 <- landbrød_data_train %>%
  model(ETS(Landbrød ~ error("A") + trend("N") + season("A")))
report(fit1)

fit1 %>% forecast(h=118) %>% autoplot(slice(landbrød_data, (n()-180):n()))
fc1 <- fit1 %>% forecast(h=118)

# Generate forecasts and compare accuracy over the test set
fc1 <- fit1 %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc1[,c("RMSE","MAE","MAPE","MASE")]

# residuals for the best ETS
fit1 %>% gg_tsresiduals()



# ANN

fit1.5 <- landbrød_data_train %>%
  model(ETS(Landbrød ~ error("A") + trend("N") + season("N")))
report(fit1.5)

fit1.5 %>% forecast(h=118) %>% autoplot(slice(landbrød_data_test, (n()-118):n()))
fc1.5 <- fit1.5 %>% forecast(h=118)

# Generate forecasts and compare accuracy over the test set
fc1.5 <- fit1.5 %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc1.5[,c("RMSE","MAE","MAPE","MASE")]


# AAA

fit2 <- landbrød_data_train %>%
  model(ETS(Landbrød ~ error("A") + trend("A") + season("A")))
report(fit2)

fit2 %>% forecast(h=118) %>% autoplot(slice(landbrød_data_test, (n()-118):n()))

# Generate forecasts and compare accuracy over the test set
fc2 <- fit2 %>% forecast(h=118) %>%
  accuracy(landbrød_data) 
fc2[,c("RMSE","MAE","MAPE","MASE")]


# AAN (Holt's method)

fit3 <- landbrød_data_train %>%
  model(ETS(Landbrød ~ error("A") + trend("A") + season("N")))
report(fit3)

fit3 %>% forecast(h=118) %>% autoplot(slice(landbrød_data_test, (n()-118):n()))

# Generate forecasts and compare accuracy over the test set
fc3 <- fit3 %>% forecast(h=118) %>%
  accuracy(landbrød_data) 
fc3[,c("RMSE","MAE","MAPE","MASE")]

# AAdN (Damped Holt's method)

fit4 <- landbrød_data_train %>%
  model(ETS(Landbrød ~ error("A") + trend("Ad") + season("N")))
report(fit4)

fit4 %>% forecast(h=118) %>% autoplot(slice(landbrød_data_test, (n()-118):n()))

# Generate forecasts and compare accuracy over the test set
fc4 <- fit4 %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc4[,c("RMSE","MAE","MAPE","MASE")]


# AAdA (just for the lols)

fit4.5 <- landbrød_data_train %>%
  model(ETS(Landbrød ~ error("A") + trend("Ad") + season("A")))
report(fit4.5)

fit4.5 %>% forecast(h=118) %>% autoplot(slice(landbrød_data_test, (n()-118):n()))

# Generate forecasts and compare accuracy over the test set
fc4.5 <- fit4.5 %>% forecast(h=118) %>%
  accuracy(landbrød_data)
fc4.5[,c("RMSE","MAE","MAPE","MASE")]


```


# ADDING WEATHER DATA TO THE BEST ARIMA MODEL

```{r}

#### (1,1,1)(1,1,1)[7] with mean temperature


fit <- Arima(landbrød_data_train$Landbrød, order=c(1,1,1), xreg=landbrød_data_train$mean_temp, 
                  seasonal=list(order=c(1,1,1), period=7))

# Generate forecasts and compare accuracy over the test set

fc <- forecast(fit, h=118, xreg = landbrød_data_test$mean_temp)

pred_vals <- fc$mean[1:118]
accuracy(pred_vals, landbrød_data_test$Landbrød)


#### (1,1,1)(1,1,1)[7] with mean temperature


fit <- Arima(landbrød_data_train$Landbrød, order=c(1,1,1), #xreg=landbrød_data_train$mean_pressure, 
                  seasonal=list(order=c(1,1,1), period=7))

# Generate forecasts and compare accuracy over the test set

fc <- forecast(fit, h=118
               #, xreg = landbrød_data_test$mean_pressure
               )


pred_vals <- fc$mean[1:118]
act_vals <- landbrød_data_test$Landbrød

accuracy(pred_vals, act_vals)


pred_vs_act <- landbrød_data_test
pred_vs_act <- subset(pred_vs_act, select=c(day,Landbrød))
pred_vs_act$Landbrød_predict <- pred_vals

pred_vs_act_tsibble <- as_tsibble(pred_vs_act)

actual_tsibble <- subset(pred_vs_act_tsibble, select=c(day,Landbrød))
actual_ts <- as.ts(actual_tsibble)

predict_tsibble <- subset(pred_vs_act_tsibble, select=c(day,Landbrød_predict))
predict_ts <- as.ts(predict_tsibble)


pred_vs_act_tsibble %>%
  autoplot(Landbrød) +
    labs(title = "Sales of landbrød", subtitle = "subtitle") +
    xlab("Year") +
    ylab("Daily number of sales")

pred_vs_act_tsibble %>%
  autoplot(Landbrød_predict) +
    labs(title = "Sales of landbrød", subtitle = "subtitle") +
    xlab("Year") +
    ylab("Daily number of sales")



par(mfrow=c(1,1))
ts.plot(as.matrix(actual_ts), type="l", col="red", ylim(0,60))
par(new=TRUE)
ts.plot(act_vals, type="l", col="green" )

```


# Using the ARIMA(1,1,1)(1,1,1)[7] model with croissant data

```{r}

croissant_data <- tsibble %>%
  select(Croissant) 

croissant_data[is.na(croissant_data)] <- 0


# Set training data from 2016 to 2019
croissant_data_train <- croissant_data %>%
  filter_index("2016" ~ "2019")

# Set test set data from 2016 to 2019
croissant_data_test <- croissant_data %>%
  filter_index("2020" ~ "2021")



# ARIMA(1,1,1)(1,1,1)[7]
fit <- croissant_data_train %>%
  model(
    arima = ARIMA(Croissant ~ pdq(1,1,1) + PDQ(1,1,1))
  )
report(fit)
fit %>% forecast(h=118) %>% autoplot(slice(croissant_data, (n()-170):n()))   # plot this fit as forecast

# Generate forecasts and compare accuracy over the test set
fc <- fit %>% forecast(h=118) %>%
  accuracy(croissant_data)
fc[,c("RMSE","MAE","MAPE","MASE")]


# How about Auto-arima on croissant?

# AUTO ARIMA
fit.arima <- auto.arima(croissant_data_train, seasonal = TRUE, ic = "aicc")    # auto arima with forced seasonality
fit.arima

# Gives us ARIMA(1,1,1)(0,0,2)[7]
# Let's make a forecast using this:


# ARIMA(1,1,1)(0,0,2)[7] 
fit <- croissant_data_train %>%
  model(
    arima = ARIMA(Croissant ~ pdq(1,1,1) + PDQ(0,0,2))
  )
report(fit)
fit %>% forecast(h=118) %>% autoplot(slice(croissant_data, (n()-170):n()))   # plot this fit as forecast

# Generate forecasts and compare accuracy over the test set
fc <- fit %>% forecast(h=118) %>%
  accuracy(croissant_data)
fc[,c("RMSE","MAE","MAPE","MASE")]



```


# Using the ARIMA(1,1,1)(1,1,1)[7] model with Almond croissant data

```{r}

almond_croissant_data <- tsibble %>%
  select(Almond_Croissant) 

almond_croissant_data[is.na(almond_croissant_data)] <- 0


# Set training data from 2016 to 2019
almond_croissant_data_train <- almond_croissant_data %>%
  filter_index("2016" ~ "2019")

# Set test set data from 2016 to 2019
almond_croissant_data_test <- almond_croissant_data %>%
  filter_index("2020" ~ "2021")

par(mfrow=c(2,1))

# BEST MODEL SO FAR ARIMA(1,1,1)(1,1,1)[7]
fit <- almond_croissant_data_train %>%
  model(
    arima = ARIMA(Almond_Croissant ~ pdq(1,1,1) + PDQ(1,1,1))
  )
report(fit)
fit %>% forecast(h=118) %>% autoplot(slice(almond_croissant_data, (n()-170):n()))   # plot this fit as forecast

# Generate forecasts and compare accuracy over the test set
fc <- fit %>% forecast(h=118) %>%
  accuracy(almond_croissant_data)
fc[,c("RMSE","MAE","MAPE","MASE")]


# How about Auto-arima on almond croissant?

# AUTO ARIMA
fit.arima <- auto.arima(almond_croissant_data_train, seasonal = TRUE, ic = "aicc")    # auto arima with forced seasonality
fit.arima

# Gives us ARIMA(1,1,1)(0,0,2)[7] 
# Let's make a forecast using this:

# ARIMA(1,1,1)(0,0,2)[7]
fit <- almond_croissant_data_train %>%
  model(
    arima = ARIMA(Almond_Croissant ~ pdq(1,1,1) + PDQ(0,0,2))
  )
report(fit)
fit %>% forecast(h=118) %>% autoplot(slice(almond_croissant_data, (n()-170):n()))   # plot this fit as forecast

# Generate forecasts and compare accuracy over the test set
fc <- fit %>% forecast(h=118) %>%
  accuracy(almond_croissant_data)
fc[,c("RMSE","MAE","MAPE","MASE")]



```



